### 2010-07-09 Thesis/Resume.tex
Added directory for PhD thesis
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@122 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\cleardoublepage

\begin{vcenterpage}
\noindent\rule[2pt]{\textwidth}{0.5pt}
\begin{center}
{\large\textbf{Real-time soft tissue modelling on GPU for medical simulation\\}}
\end{center}
{\large\textbf{Abstract:}}
Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla. Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.
\\
Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla. \\

@@

Blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla.
\\
{\large\textbf{Keywords:}}
Medical simulation, soft tissue modelling, finite element method, GPU
\\
\noindent\rule[2pt]{\textwidth}{0.5pt}
\end{vcenterpage}

>>>>

\chapter*{Résumé}

\large\textbf{Simulation de tissus mous en temps réel sur GPU pour la simulation médicale} \\

Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla. Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.
\\
Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla. \\

@@

Blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla, blablablablabla bla blabla bla blablablabla bla.Blablabla bla blabla blablablabla.
